### 2016-10-04 HSF-TN/draft-2016-VACPLAT/draft-HSF-TN-2016-VACPLAT.tex
.

\usepackage{microtype}
\usepackage{lineno}    % Line numbering during drafting
\usepackage{xspace}    % Avoid problems with missing or double spaces after predefined symbold
\usepackage{caption}   % These three command get the figure and table captions automatically small
\renewcommand{\captionfont}{\small}
\renewcommand{\captionlabelfont}{\small}

@@

%%%% Uncomment next 2 lines if desired
%\tableofcontents
%\cleardoublepage

@@

%% Uncomment during drafting and review.
%% Comment before a final submission.
\linenumbers

@@

This note is written in terms of VMs, but the interfaces have been 
designed to be generalised to other forms of logical machine in the
future, such as Docker containers and unikernels.

@@

@@

\begin{center}
\begin{table}[h]
\label{table:shutdowncodes}
\begin{center}
\begin{tabular}{l}
\\
100 Shutdown as requested by the VM's host/hypervisor \\
200 Intended work completed ok \\
300 No more work available from task queue \\
400 Site/host/VM is currently banned/disabled from receiving more work \\
500 Problem detected with environment/VM provided by the site \\
600 Grid-wide problem with job agent or application within VM \\
700 Transient problem with job agent or application within VM \\
\\
\end{tabular}
\caption{\label{opt}Shutdown codes and messages}
\end{center}
\end{table}
\end{center}

@@

If the VM requires an X.509 proxy, it must expect that the special pattern
\texttt{\#\#user\_data\_option\_x509\_proxy\#\#} will be replaced by the 
PEM encoded X.509 certificates and RSA private key which compromise the
proxy. VMLM's should provide a mechanism for creating X.509 proxies
dynamically for each VM instance from a host or robot certificate owned
by the resource provider, with an X.509 proxy lifetime reflecting
the maximum VM lifetime.

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``factory\_status''
\item[vac\_version] Name and software version of Vac
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[num\_machines] Number of machine\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machine] Hostname of the VM slot
\item[state] State of the current or most recent VM in this slot, as a string
\item[uuid] Lowlevel UUID, as used by libvirtd
\item[created\_time] Unix time of the VM's creation
\item[started\_time] Unix time the VM entered the running state
\item[heartbeat\_time] Unix time when the VM was last observed to be running (this is not the same as any heartbeat generated within the VM)
\item[cpu\_seconds] CPU seconds used by the VM
\item[cpu\_percentage] Recent CPU percentage use. May be over 100\% for mulitprocessor VMs
\item[hs06] Total HEPSPEC06 for the processors assigned to this VM
\item[machinetype] Name of the machinetype
\item[shutdown\_message] Any shutdown message given by the last VM to run in this slot
\item[shutdown\_time] Unix time of the shutdown\_message
\end{description}
\end{quote}

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``factory\_status''
\item[vac\_version] Name and software version of Vac
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[num\_machinetypes] Number of machinetype\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machinetype] Name of the machinetype
\item[running\_hs06] Total HEPSPEC06 of all the processors allocated to running VMs for this machinetype on this factory
\item[running\_machines] Number of running VMs for this machinetype on this factory
\item[running\_cpus] Number of CPUs allocated to running VMs for this machinetype on this factory
\item[num\_before\_fizzle] Number of running VMs which have not yet reached fizzle\_seconds
\item[shutdown\_message] Shutdown message given by the most recently created VM for this machinetype on this factory which has finished
\item[shutdown\_time] Unix time of the shutdown\_message
\item[shutdown\_machine] Name of the VM slot associated with the shutdown\_message
\end{description}
\end{quote}

@@

\section{GLUE2}
\label{sec:glue2}

VMLMs should publish status information as JSON documents using the GLUE 2.0 
schema, at an HTTPS URL advertised in the GOCDB service entry for the space,
in the Grid Information / URL field.

\clearpage

@@

Vacuum platform interfaces have been described ...

>>>>

\usepackage{float}
\usepackage{microtype}
\usepackage{lineno}    % Line numbering during drafting
\usepackage{xspace}    % Avoid problems with missing or double spaces after predefined symbold
\usepackage{caption}   % These three command get the figure and table captions automatically small
\renewcommand{\captionfont}{\small}
\renewcommand{\captionlabelfont}{\small}

@@

%%%% Uncomment next 2 lines if desired
\tableofcontents
%\cleardoublepage

@@

%% Uncomment during drafting and review.
%% Comment before a final submission.
%\linenumbers

@@

This note is written in terms of VMs, but the interfaces have been 
designed to be generalise to other forms of logical machine in the
future, such as Docker containers and unikernels.

@@

Each space is occupied by VMs which are instances of one or more 
``machinetype'' that the VMLM is able to create. Each machinetype
corresponds to a specific combination of VM boot image and 
contextualization.

@@

\begin{center}
\begin{table}[H]
\label{table:shutdowncodes}
\begin{center}
\begin{tabular}{l}
\\
100 Shutdown as requested by the VM's host/hypervisor \\
200 Intended work completed ok \\
300 No more work available from task queue \\
400 Site/host/VM is currently banned/disabled from receiving more work \\
500 Problem detected with environment/VM provided by the site \\
600 Grid-wide problem with job agent or application within VM \\
700 Transient problem with job agent or application within VM \\
\\
\end{tabular}
\caption{\label{opt}Shutdown codes and messages}
\end{center}
\end{table}
\end{center}

@@

If the VM requires an X.509 proxy, it must expect that the special pattern
\texttt{\#\#user\_data\_option\_x509\_proxy\#\#} will be replaced by the 
PEM encoded X.509 certificates and RSA private key which compromise the
proxy. VMLMs should provide a mechanism for creating X.509 proxies
dynamically for each VM instance from a host or robot certificate owned
by the resource provider, with an X.509 proxy lifetime reflecting
the maximum VM lifetime.

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``machine\_status''
\item[vac\_version] Name and software version of Vac
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[num\_machines] Number of machine\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machine] Hostname of the VM slot
\item[state] State of the current or most recent VM in this slot, as a string
\item[uuid] Lowlevel UUID, as used by libvirtd
\item[created\_time] Unix time of the VM's creation
\item[started\_time] Unix time the VM entered the running state
\item[heartbeat\_time] Unix time when the VM was last observed to be running (this is not the same as any heartbeat generated within the VM)
\item[cpu\_seconds] CPU seconds used by the VM
\item[cpu\_percentage] Recent CPU percentage use. May be over 100\% for mulitprocessor VMs
\item[hs06] Total HEPSPEC06 for the processors assigned to this VM
\item[machinetype] Name of the machinetype
\item[shutdown\_message] Any shutdown message given by the last VM to run in this slot
\item[shutdown\_time] Unix time of the shutdown\_message
\end{description}
\end{quote}

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``machinetype\_status''
\item[vac\_version] Name and software version of Vac
\item[vacquery\_version] Name and version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[num\_machinetypes] Number of machinetype\_status messages to expect from this factory
\item[time\_sent] Time in Unix seconds
\item[machinetype] Name of the machinetype
\item[running\_hs06] Total HEPSPEC06 of all the processors allocated to running VMs for this machinetype on this factory
\item[running\_machines] Number of running VMs for this machinetype on this factory
\item[running\_cpus] Number of CPUs allocated to running VMs for this machinetype on this factory
\item[num\_before\_fizzle] Number of running VMs which have not yet reached fizzle\_seconds
\item[shutdown\_message] Shutdown message given by the most recently created VM for this machinetype on this factory which has finished
\item[shutdown\_time] Unix time of the shutdown\_message
\item[shutdown\_machine] Name of the VM slot associated with the shutdown\_message
\end{description}
\end{quote}

@@

%\section{GLUE2}
%\label{sec:glue2}
%
%VMLMs should publish status information as JSON documents using the GLUE 2.0 
%schema, at an HTTPS URL advertised in the GOCDB service entry for the space,
%in the Grid Information / URL field.

%\clearpage

@@

This note has described the various interfaces between virtual machines and
virtual machine lifecycle managers required by the Vacuum Platform. Three new
interfaces (\$JOBOUTPUTS, VacQuery, and VacUserData) have been introduced,
and requirements set out for the use of Machine/Job Features, APEL, and
GOCDB with the platform. Procedures for how experiments providing VMs should
present their VM boot images and contextualization are also explained.
